\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,hyperref,fancyvrb}
\title{CSCI 202, Spring 2017, Project}
\author{Geoffrey Matthews}

\begin{document}
\maketitle

\begin{description}

\item[Due date:] Midnight, Friday, June 2.

\item[Goals:] Exercise creativity in developing a dynamic web page.
  

\item[Zip your folder:]
  Put all your files (including the supporting files) in a single
  folder and  make a compressed (zip) archive of the folder.

\item[Be creative!]  For this assignment, you have to design a web
  site and use the skills you've learned in this class to make it
  dynamic.  In particular, you must use
  \begin{itemize}
  \item HTML
  \item CSS
  \item Javascript, including loops and arrays.
  \end{itemize}
  Note: PHP is optional.

\item[Minimal requirements:] There are no minimal
  requirements. Depending on what kind of web page you make, different
  grading criteria are appropriate.  I'll be looking for creativity
  and effort appropriate for the time you've been given.

  If you have trouble being that creative, you can get full credit
  with the following.  Note that these are {\em not} necessary for
  this assignment, they are merely {\em sufficient} for full credit:
  \begin{itemize}
  \item At least five pages.
  \item A navigation bar.
  \item Responsiveness to page width using media queries.
  \item At least two javascript arrays and for loops to process them.
  \item At least ten style  classes or ids.
  \item A consistent and attractive look and feel (styling) to all the
    pages. 
  \end{itemize}

\item[Suggestions:]\mbox{}
  \begin{itemize}
  \item
    Make a game.
    \begin{itemize}
      \item The penguins and yeti game from the
    last two labs makes a good starting point.  You can add scoring,
    win/lose, two players taking turns, sound effects, {\em etc.}
  \item A puzzle game such as a crossword or sudoku is fairly easy.
    \end {itemize}
  \item
    Make a professional web site about yourself.
  \item
    Make a fan site about your favorite movie.
  \end{itemize}
\end{description}

\end{document}
